### 2017-02-27 2017mergingmerges/section/05-Evaluation.tex
Talk about drop instructions

% -----------------------------------------------------------------------------
\subsection{Optimisation with Drop Instructions}
\label{s:Optimisation}
After we have fused two processes together, it may be possible to simplify the result before fusing in a third. Consider the result of fusing @group@ and @merge@ which we saw back in Fig.\ref{fig:Process:Fused}. At labels @F1@ and @F2@ are @jump@ instructions, where the first passes control to the second. The update expressions attached to these instructions are also non-interferring, which means we can safely combine these consecutive @jump@ instructions into a single @jump@ to @F4@. There are also @jump@ instructions like the one at @F5@ which have no associated update expressions, and thus can be eliminated completely. We can also perform constant propagation, which in this case would allow us to eliminate the first @case@ instruction.

Minimising the number of states in intermediate processes has a follow-on effect in that the final fused result has a lower number of states. Provided we do not change the order of instructions that do not require synchronization with other processes, meaning @pull@ @push@ or @drop@, the fusability of the overall process network will not be affected.

Another useful optimization is to notice that in some cases, when a heap variable is updated it is always assigned the value of another variable. In Fig.\ref{fig:Process:Fused}, the @v@ and @x1@ variables are only ever assigned the value of @b1@, and @b1@ itself is only ever loaded via a @pull@ instruction. Remember from \S\ref{s:Fusion:FusingPulls} that the variable @b1@ is the stream buffer variable. Values pulled from stream @sIn1@ are first stored in @b1@ before being copied to @v@ and @x1@. When the two processes to be fused share a common input stream, use of stream buffer variable allows one process to continue using the value that was last pulled from the stream, while the other moves onto the next one.

When the two processes to be fused are able to accept the next variable from the stream at the same time, there is no need for the separate stream buffer variable. In this case we can perform a copy-propagation optimisation, replacing all occurrences of @v@ and @x1@ with the single variable @b1@.

>>>>

% -----------------------------------------------------------------------------
\subsection{Optimisation and Drop Instructions}
\label{s:Optimisation}
After we have fused two processes together, it may be possible to simplify the result before fusing in a third. Consider the result of fusing @group@ and @merge@ which we saw back in Fig.\ref{fig:Process:Fused}. At labels @F1@ and @F2@ are @jump@ instructions, where the first passes control to the second. The update expressions attached to these instructions are also non-interferring, which means we can safely combine these consecutive @jump@ instructions into a single @jump@ to @F4@. In general, we prefer to have @jump@ instructions from separate processes scheduled into consecutive groups, rather than spread out through the result code. The (PreferJump) clauses of Fig.\ref{fig:Fusion:Def:StepPair} implement a heuristic that causes jump instructions to be scheduled before all others, so they tend to end up in these groups.

There are also @jump@ instructions like the one at @F5@ which have no associated update expressions, and thus can be eliminated completely. Another simple optimization is to perform constant propagation, which in this case would allow us to eliminate the first @case@ instruction.

Minimising the number of states in an intermediate process has the follow-on effect that the final fused result also has lower number of states. Provided we do not change the order of instructions that do not require synchronization with other processes, meaning @pull@ @push@ or @drop@, the fusability of the overall process network will not be affected.

Another optimization is to notice that in some cases, when a heap variable is updated it is always assigned the value of another variable. In Fig.\ref{fig:Process:Fused}, the @v@ and @x1@ variables are only ever assigned the value of @b1@, and @b1@ itself is only ever loaded via a @pull@ instruction. Remember from \S\ref{s:Fusion:FusingPulls} that the variable @b1@ is the stream buffer variable. Values pulled from stream @sIn1@ are first stored in @b1@ before being copied to @v@ and @x1@. When the two processes to be fused share a common input stream, use of stream buffer variable allows one process to continue using the value that was last pulled from the stream, while the other moves onto the next one.

When the two processes are able to accept the next variable from the stream at the same time, there is no need for the separate stream buffer variable. This is the case in Fig.\ref{fig:Process:Fused}, and we can perform a copy-propagation optimisation, replacing all occurrences of @v@ and @x1@ with the single variable @b1@. In the result, the interleaved instructions from both source processes then share the same heap variable.

To increase the chance that we can perform this above copy-propagation, we need both processess to want to pull from the same stream at the same time. In the definition of a particular process, moving the @drop@ instruction for a particular stream as late as possible prevents a @pull@ instruction from a second process being scheduled in too early. In general, the @drop@ for a particlar stream should be placed just before a @pull@ from the same stream.
